|

### 2021-03-17 appendix/appendix.Rmd
fix meta-regression first check

@@

In this section, we show the coefficients for our meta-regressions. We start with expenditure as a percentage of GDP as the dependent variable.

@@

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- permutest(mod, progbar = F)
mod
```

@@

1.  Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
2.  Year has null effect.
3.  Unpublished papers tend to have higher coefficients than published papers.
4.  Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
5.  In terms of modelling, passing from `OLS` to `PANEL` increases the detected effects.
6.  When passing from `Country` to `Cross-Country`, it has no effect on the estimated coefficients.

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- permutest(mod, progbar = F)
mod
```

@@

1.  Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
2.  Year has a positive effect: the younger the publication, the higher the detected coefficient.
3.  Unpublished papers tend to have higher coefficients than published papers.
4.  Passing from `Majoritarian` to `Non-Majoritarian` significantly decreases the effects found in our models.
5.  Regarding statistical models, passing from `OLS` to `PANEL` increases the detected effects.

Here we do the same exercise with expenditure per capita as the main outcome.

```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear,
            control=list(maxiter=1000))
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
mod <- permutest(mod, progbar = F)
mod
```

We have the following results for the meta-regressions of Expenditure Per Capita:

1.  Compared with `K`, models with `N` tend to detect significantly smaller effects.
2.  Year has null effect.
3.  `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
4.  Regarding statistical models, passing from `OLS` to `PANEL` or `IV` increases the detected effects.

We also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)
summary(mod)
```

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- permutest(mod, progbar = F, iter = 100)
mod
```

With all coefficients, the results of the effect sizes on the Expenditure Per Capita regressions are the following:

1.  Compared with `K`, models with `N` tend to detect significantly smaller effects.
2.  Year has now a positive effect on coefficient sizes.
3.  `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
4.  Regarding statistical models, passing from `OLS` to `PANEL` decreases the detected effects.
5.  All other coeffients were not significant.

Lastly, we run the model with the natural logarithm of expenditure per capita.

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- permutest(mod, progbar = F)
mod
```

For the meta-regressions of Log of Expenditure Per Capita we find no significant results.

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ indepvar2+year+published+elecsys2+method,
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)
summary(mod)
```

```{r, warning=F, cache=T, echo = FALSE}
mod <- permutest(mod, progbar = F)
```

1.  In terms of the modelling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
2.  All other coefficients remained insignificant.

@@

1.  The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
2.  The type of the independent variable in the study ($N$, $K$, $log (N)$);
3.  The electoral system (Majoritarian, Proportional Representation, and Mixed).

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <-  rma(yi = coef,
              sei = SE,
              data = dat,
              method = "REML",
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
              test = "knha")
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, size="footnotesize", cache=T, echo = FALSE}
permutest(mod, progbar = F)
```

In the main text, we selected coefficients based on the regressions that had most observations and presented a full model (with fixed effects or intermediate bandwidth in RDD). We also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma(yi = coef,
              sei = SE,
              data = fulldat,
              method = "REML",
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
              test = "knha")
summary(mod)
```

```{r, size="footnotesize", cache=T, echo = FALSE}
permutest(mod, progbar = F)
```

```{=html}
<!---
# Auxiliary Functions

## Webscraping Code
\label{sub:scrap}

The code we used to download the articles cited in our paper are in the appendix, under the file name `building_metadata_dataset.R`. --->
```
# Session Information

>>>>

In the meta-regressions, we study the effects of a group of moderators on the reported government spending data. We select the following moderators:

1. The independent variable (variable `indepvar2`):
  - `K`: Upper House Size
  - `N`: Lower House Size
  - `logN`: Log of Lower House Size

2. Year that the paper was published (for working papers, the year it was posted online; variable `year`)

3. A dummy indicating whether the paper was published or not (variable `published`).

4. A dummy for non-majoritarian electoral systems (variable `elecsys2`).

5. The estimation method used in the papers (variable `method`):
  - `OLS`: Ordinary-Least Squares in Cross-Sectional data.
  - `PANEL`: Time-Series Cross-Section models, with estimated fixed effects.
  - `IV`: Instrumental Variables models.
  - `RDD`: Regression Discontinuity Designs.

The results follows below, for the three combinations of dependent variables: Expenditure Per Capita, Log of Expenditure Per Capita, and Expenditure as a Percentage of the GDP.

Here we study the expenditure per capita as the main outcome, aggregating all types of independent variables.

```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              subset = dat$depvar2=='ExpPC',
              slab = dat$authoryear)

For the meta-regressions of Expenditure Per Capita, we find no significant moderator. We also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              subset = fulldat$depvar2=='ExpPC',
              slab = fulldat$authoryear)

summary(mod)
```
With all coefficients, the results of the effect sizes on the Expenditure Per Capita regressions are the following:

1.  Compared with `K`, models with `N` tend to detect significantly smaller effects.

2.  Year has now a positive effect on coefficient sizes.

3.  All other coeffients were not significant.

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              subset = dat$depvar2=='logExpPC',
              slab = dat$authoryear)

The only significant result points that published papers tend to report a smaller coefficient than unpublished papers.

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~indepvar2+year+published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              subset = fulldat$depvar2=='logExpPC',
              slab = fulldat$authoryear)

1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.

2. Having the log of lower house seats (`logN`) as the main independent variable increases the detected effect.

All other results are insignificant.

@@

@@

@@

1. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.

2. All other moderators remain insignificant.

@@

@@

1. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.

2. All other moderators remain insignificant.

@@

1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP).

2. The type of the independent variable in the study (lower house size, upper house size, or log of lower house size).

3. The electoral system (Majoritarian versus Non-Majoritarian).

4. The year when the study was published.

5. Whether the study is a working paper or published work.

6. The estimation method used in the paper (OLS, PANEL, IV, or RDD).

@@

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = dat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+
                published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              slab = dat$authoryear)

summary(mod)
```
In the restricted model, with only the main coefficients in the selected papers, no moderator has a significant effect. We also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
mod <- rma.mv(yi = coef,
              V = VAR,
              data = fulldat,
              method = "REML",
              random = ~ 1 | id_level1/id_level2, 
              mods = ~depvar2+indepvar2+year+
                published+elecsys2+method,
              test = "knha",
              tdist = TRUE,
              slab = fulldat$authoryear)
summary(mod)
```
In the full model, we can see that:

1. For the dependent variable, models with Log of Per Capita Expenditure tend to report significantly smaller effects than models with Per Capita Expenditure.

2. For the independent variable, models with Log of Lower House Size tend to report significantly larger effects than models with Upper House Size.

3. Over time, the reported coefficients have been increasing in size.

4. Compared with OLS, Panel and RDD report significantly smaller coefficients.

5. All other moderators are insignificant.

# Session Information
